\bf On semidefinite-representable sets over valuation fields

### 2025-03-17 article/paper_padic_spec.tex
commit by Simone

\author{Corentin Cornou$^{1}$, Simone Naldi$^{2,3}$ and Tristan Vaccon$^{2}$}

\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay, France.}
\footnotetext[2]{Université de Limoges, CNRS, XLIM, UMR 7252, F-87000 Limoges, France.}
\footnotetext[3]{Sorbonne Université, CNRS, LIP6, Equipe PolSys, F-75005 Paris, France.}

@@

\begin{abstract}
  \noindent
  Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
  of linear programming (LP) and semidefinite programming (SDP) and form the family of
  semidefinite-representable sets. This paper investigates versions of these sets and of
  the related optimization problems with data over a field $K$ with valuation.
  We prove that basic properties of semidefinite-representable sets generalize to this setting.
  We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
  representable over $K$ but are not $K$-spectrahedra.
\end{abstract}

@@

>>>>

\author{Corentin Cornou$^{1}$, Simone Naldi$^{2}$ and Tristan Vaccon$^{2}$}

\footnotetext[1]{ENS Paris-Saclay, Université Paris-Saclay, France.}
\footnotetext[2]{Université de Limoges, CNRS, XLIM, UMR 7252, F-87000 Limoges, France.}
%\footnotetext[3]{Sorbonne Université, CNRS, LIP6, Equipe PolSys, F-75005 Paris, France.}

@@

\begin{abstract}
  \noindent
  Real polyhedra and real spectrahedra (or their projections) are respectively the feasible sets
  of linear and semidefinite programming, and form the family of
  semidefinite-representable sets. This paper investigates versions of these sets and of
  the related optimization problems with data over a field $K$ with valuation.
  We prove that basic properties of semidefinite-representable sets generalize to this setting.
  We showcase examples of non-polyhedral $K$-spectrahedra and of sets that are semidefinite
  representable over $K$ but are not $K$-spectrahedra.
\end{abstract}

@@

Linear programming

A natural generalization of LP is {\it semidefinite programming}

Contrary to the LP case, the complexity status of SDP is mostly open.

Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral}.
